How it's been doing a statistics PhD plus some research

### 2022-09-19 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
ea-talk upload

```{r echo=FALSE}
knitr::include_graphics("depends/model-direct-benefits-h.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("geometry-graph-zwe.pdf")
```

@@

```{r echo=FALSE}
knitr::include_graphics("depends/infections-averted-country.pdf")
```

>>>>

```{r echo=FALSE}
knitr::include_graphics("depends/model-direct-benefits.pdf")
```

@@

```{r echo=FALSE}
library(bsae)
plot_graph(zw, add_geography = TRUE)
```

@@

```{r echo=FALSE}
knitr::include_graphics("depends/infections-reached-country.pdf")
```
